---
title: "Successuful Aging"
author: Natália Scoralick and Elizabeth do Nascimento - Universidade Federal de Minas
  Gerais
date: "15 de maio de 2016"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 9
    keep_md: yes
    toc: yes
---

#Successuful Aging

All files used here are availible in a public repository licensed under MIT Licences and accessible by the following url:

https://github.com/crepeia/saging

You can access the final report here:

http://rpubs.com/leomartinsjf/saging

Statistics consulting work was made by Leonardo Fernandes Martins. If you need help to understand, reproduce or cite this analysis - reach me out at:

leomartinsjf@gmail.com



#Loading required packages
```{r First, message=FALSE, warning=FALSE, include=FALSE}
require(foreign) # Read data stored SPSS
require(car) #Recode Variables
require(psych) #Psychometrics
require(lavaan) #Confirmatory and SEM
require(semPlot) # Plots for SEM
require(semTools) # Comparing SEM models
require(ggplot2) # Plots
require(gvlma) # Regression Assumptions 
require(QuantPsyc) # Beta Coefficients
require(Hmisc) # Regression Diagnostic
require(MASS) # Confidence Interval for Model Parameter
library(htmlTable) # Generating Tables - easy to copy and paste
library(plyr) # Simple Rounding 

# Some packages are listed but were not used here 

```

#Preparing all data
```{r Second, message=FALSE, warning=FALSE, include=T}
#Setting Directory
setwd("~/successful_aging")

#Importing SPSS file .sav
base.dat <- read.spss("Base.sav", to.data.frame = T, use.missings = T)
```


#Selecting only working variables
```{r, message=FALSE, warning=FALSE, include=T}
saging <- base.dat[ ,c(3,6:27)]


saging <- base.dat[ ,c(2,4,5,6,7,8,9,3,10:27)]

#As dataframe
saging<-as.data.frame(saging)

#As factor

saging[,c(1)]<-as.factor(saging[,c(1)])
saging[,c(2)]<-as.factor(saging[,c(2)])
saging[,c(3)]<-as.factor(saging[,c(3)])
saging[,c(4)]<-as.factor(saging[,c(4)])
saging[,c(5)]<-as.factor(saging[,c(5)])
saging[,c(6)]<-as.factor(saging[,c(6)])
saging[,c(7)]<-as.factor(saging[,c(7)])

saging<-as.data.frame(saging)

#As numeric
for (i in c(7:26)) {
saging[,c(i)]<-as.numeric(saging[,c(i)])
}

#Sabedoria
saging$sabed<- saging$X.3dwscogAFC + saging$X.3dwsrefAFC + saging$X.3dwsafeAFC
```

#Variables Summary - Descriptive Stats
```{r}
#Status Social Economic - Variables

##Descriptive 
describe(saging)
summary(saging)
```

#Correlations among study variables
```{r}
sagingcorr <- saging[ ,c("esvtotal", "autosaude", "gdstotal", "voctotal", "rmtotal", "qsvbusca", "qsvpresenca", "X.3dwstotalAFC", "qcspatotal")]
#r<-tcor$r 
#r <- txtRound(r, 2) 
#r
#htmlTable(r)

sagingcorr[,c("autosaude")]<-as.numeric(sagingcorr[,c("autosaude")])
tcor<-corr.test(sagingcorr)

#p<-tcor$p
#p <- txtRound(p, 2)
#p
#htmlTable(p) - only 
```


#Structural Model 
```{r}
#Saging Model 

saging1 <- '
# measurement model
envels =~ esvtotal + autosaude + gdstotal


# regressions
envels ~ voctotal + rmtotal + qsvbusca + qsvpresenca + X.3dwstotalAFC + qcspatotal


#Correlations and Residuals 

gdstotal ~~ gdstotal 
esvtotal ~~ esvtotal
autosaude ~~ autosaude
envels ~~ envels
'

#Model Fit
fitsaging1 <- sem(saging1, estimator="WLSMVS", mimic = "Mplus", data = saging,
        ordered=c("autosaude"))

#Model Summary 
summary(fitsaging1, standardized=T, fit.measures=T, rsquare=T)

#Model Fit Measures
fitMeasures(fitsaging1, c("chisq","df","rmsea","rmsea.ci.lower", "rmsea.ci.upper", "srmr", "cfi", "tli", "nfi", "ecvi"))
moreFitIndices(fitsaging1, fit.measures = "all", nPrior = 303)

#Parameters Estimates
EstPCA2rf <- parameterEstimates(fitsaging1, standardized=T, ci=F)
subset(EstPCA2rf, op == "=~")

#q <- txtRound(EstPCA2rf, 2) - Short script to genarete easy copy and paste tables
#q
#htmlTable(q)

#Modification Index
MIPCA2rf<-modindices(fitsaging1)
MIIPCA2rf<- MIPCA2rf[which(MIPCA2rf$mi>10),]
print(MIIPCA2rf)
```


```{r}
#Model Plot
semPaths(fitsaging1, what="path", whatLabels ="std", edge.label.cex = 0.7, exoVar = F, exoCov = T, layout = "tree2", optimizeLatRes=T, style = "lisrel", curve= 0.9, sizeLat = 5, sizeLat2 = 5, sizeMan = 3, sizeMan2 = 3, title = T, thresholds = F, curvePivot=T, intercepts = F, residuals = F)

#Define Title
title(main = "Figura 1. Modelo de Equação Estrutural para Envelhecimento Saudável(n=303)", line = 1)

#Define Subtitle
title(sub=chi^2~(31)==272.039 ~ "CFI=0.919; TLI=0.858; NFI=0.874; RMSEA=0.068; 90%CI(0.037-0.057)" , line = 3, font.sub = 1, cex.sub = 0.5)
```



